---
title: "Assignment4"
author: "Claire Madden"
date: "5/28/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(tidyverse)
data<-read_csv("HW4Data.csv")
graph_data<-read_csv("HW4Data_edited.csv")

explore_graphA <- ggplot(data, aes(x=Abatement, y=MC_A))+
  geom_point()+
  geom_smooth()

explore_graphA
# looks linear for sure

explore_graphB <- ggplot(data, aes(x=Abatement, y=MC_B))+
  geom_point()+
  geom_smooth()

explore_graphB
# logistic maybe, cubic?

explore_graphC <- ggplot(data, aes(x=Abatement, y=MC_C))+
  geom_point()+
  geom_smooth()

explore_graphC
# close to linear, maybe exponential

explore_graphD <- ggplot(data, aes(x=Abatement, y=MC_D))+
  geom_point()+
  geom_smooth()

explore_graphD
# hard to see trend, maybe linear would be closest to accurate?

```

1. Write down a plausible functional form for the marginal cost of abatement for sector A. Use regression analysis to estimate the parameters of that function. Repeating this for sectors B, C, and D will give you a model of the marginal cost of abatement function for each sector. How well do your models fit the data for each sector? You may need to experiment with different functional forms. Produce a plot of the estimated marginal abatement cost functions in all four sectors (this plot should go in your memo).
```{r}

MC_A_model <- lm(MC_A ~ Abatement, data = data)

summary(MC_A_model)

A_int <- MC_A_model$coefficients[1]
A_slope <- MC_A_model$coefficients[2]
#p-value: 1.01e-08
#R-squared: 0.904, pretty good fit

MC_B_model <- lm(MC_B ~ Abatement, data = data)
summary(MC_B_model)

B_int <- MC_B_model$coefficients[1]
B_slope <- MC_B_model$coefficients[2]
#p-value: 0.0007672
#R-squared: 0.5355, probably want to change this one for a better fit?

MC_C_model <- lm(MC_C ~ Abatement, data = data)
summary(MC_C_model)

C_int <- MC_C_model$coefficients[1]
C_slope <- MC_C_model$coefficients[2]
#p-value: 1.044e-07
#R-squared: 0.8663, pretty good will probably keep this

MC_D_model <- lm(MC_D ~ Abatement, data = data)
summary(MC_D_model)

D_int <- MC_D_model$coefficients[1]
D_slope <- MC_D_model$coefficients[2]
#p-value: 0.001121
#R-squared: 0.5108 is worst among them


a_curve <- function(x){A_int + A_slope*x}
b_curve <- function(x){B_int + B_slope*x}
c_curve <- function(x){C_int + C_slope*x}
d_curve <- function(x){D_int + D_slope*x}

mc_plot <- ggplot(data.frame(x=c(0,200)))+
  stat_function(fun=a_curve, aes(color = "A"))+
  stat_function(fun=b_curve, aes(color = "B"))+
  stat_function(fun=c_curve, aes(color = "C"))+
  stat_function(fun=d_curve, aes(color = "D"))+
  scale_x_continuous(limits = c(0,200), expand = c(0,0))+
  scale_y_continuous(limits = c(0,200), expand = c(0,0))+
  labs(fil = "", 
       color = "Sector", 
       x = "Carbon Abatement (tons of CO2)",
       y = "Price ($/ton)",
       title = "Marginal Cost of Carbon Abatement by Sector")+
  theme_classic()

mc_plot

```

2. Using these models and the current level of carbon emissions, derive each sector’s demand curve for carbon emissions. In other words, how much would each sector be willing to pay for the right to pollute the first unit, second unit, etc? Draw these demand curves on a graph. Which sector is willing to pay the most for the first unit of carbon emissions?

```{r}
#Current carbon emissions in the sectors are: (A=180, B=200, C=220, and D=300)

# Demand curve for Sector A
a_demand_int <- a_curve(180)
a_demand_slope <- (0-a_demand_int)/(180-0)
#demand curve as a function 
a_demand_curve <- function(x){
  a_demand_int + a_demand_slope*x}

q_A <- seq(0,180,by=10)
WTP_A <- a_demand_curve(q_A)
#WTP at q=1 is $95.19

# Demand curve for Sector B
b_demand_int <- b_curve(200)
b_demand_slope <- (0-b_demand_int)/(200-0)
#demand curve as a function 
b_demand_curve <- function(x){
  b_demand_int + b_demand_slope*x}

q_B <- seq(0,200,by=10)
WTP_B <- b_demand_curve(q_B)
#WTP at q=1 is $49.07

# Demand curve for Sector C
c_demand_int <- c_curve(220)
c_demand_slope <- (0-c_demand_int)/(220-0)
#demand curve as a function 
c_demand_curve <- function(x){
  c_demand_int + c_demand_slope*x}

q_C <- seq(0,220,by=10)
WTP_C <- c_demand_curve(q_C)
#WTP at q=1 is $160.79

# Demand curve for Sector D
d_demand_int <- d_curve(300)
d_demand_slope <- (0-d_demand_int)/(300-0)
# Demand curve as a function
d_demand_curve <- function(x){d_demand_int + d_demand_slope*x}

q_D <- seq(0,300,by=10)
WTP_D <- d_demand_curve(q_D)
#WTP at q=1 is $87.67


# Plot demand curves for each sector
demand_plot <- ggplot(data.frame(x=c(0,200))) + 
  stat_function(fun=a_demand_curve, geom ="line", aes(color = "A")) + 
  stat_function(fun=b_demand_curve, geom ="line", aes(color = "B")) +
  stat_function(fun=c_demand_curve, geom ="line", aes(color = "C")) +
  stat_function(fun=d_demand_curve, geom ="line", aes(color = "D")) +
  scale_x_continuous(limits =c(0,350), expand = c(0,0))+
  scale_y_continuous(limits=c(0,200), expand=c(0,0))+
  theme_classic() +
  labs(fill = "", 
       color = "Sector",
       x = "Carbon Emissions Demand (tons)",
       y = "Price ($/ton)")+
  ggtitle("Demand for Carbon Emissions by Sector") 

demand_plot

#sector willing to pay the most for the first unit of carbon emissions is C


```


3. Now focus on country X (which contains sectors A, B, and C). Assume there are no “co-benefits” from carbon abatement (i.e. that there are no local pollutants that are affected by carbon abatement). Suppose to meet the Paris Accord commitments, country X needs to cut all carbon emissions in half. For each of the policy options listed below, derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated.

a. Cap on carbon. Each sector (A, B, and C) must cut its carbon emissions by 100 tons (thus reducing total emissions from 600 down to 300).

b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.

c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.

```{r}

#Current carbon emissions in the sectors are: (A=180, B=200, C=220, and D=300)

#3a. 
#derive: (1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated

#new carbon emissions in sector (A = 80, B = 100, C= 120)

#mc_a <- a_curve(100)
#a_x_int <- a_curve1(0)
#14.99
#tc_a <- (0.5*mc_a*(100-a_x_int))
#2084.53

#mc_b <- b_curve(100)
#tc_b <- (0.5*(mc_b+B_int)*100)
#1925.49

#mc_c <- c_curve(100)
#c_x_int <- c_curve1(0)
#14.87
#tc_c <- (0.5*mc_c*(100-c_x_int))
#2840.28

#tc_all <- sum(tc_a, tc_b, tc_c)
#6850.31

# tax revenue is 0

#better way to find cost of abatement
tc_a_integrate <- integrate(a_curve, 0, 100)
tc_b_integrate <- integrate(b_curve, 0, 100)
tc_c_integrate <- integrate(c_curve, 0, 100)

tc_total <- tc_a_integrate$value + tc_b_integrate$value + tc_c_integrate$value


# for sectors A and C they are actually saving money by abating until they reach their x intercept of the mc curve
```




```{r}
#3b. Tax on carbon. To emit a ton of carbon in country X, you must pay a tax of $t. You will need to find the tax that accomplishes the desired reduction.

#(1) the total cost of meeting the target in country X, (2) the cost (or benefit) to each sector, and (3) the tax revenue generated.

#aggregate mc curve
a_int1 <- (-A_int/A_slope)
a_slope1 <- (1/A_slope)

a_curve1 <- function(x){a_int1+a_slope1*x}

b_int1 <- (-B_int/B_slope)
b_slope1 <- (1/B_slope)

b_curve1 <- function(x){b_int1+b_slope1*x}

c_int1 <- (-C_int/C_slope)
c_slope1 <- (1/C_slope)

c_curve1 <- function(x){c_int1+c_slope1*x}

d_int1 <- (-D_int/D_slope)
d_slope1 <- (1/D_slope)

d_curve1 <- function(x){d_int1 + d_slope1*x}







agg_mc_int <- sum(a_int1,b_int1,c_int1)
agg_mc_slope <- sum(a_slope1,b_slope1,c_slope1)

agg_mc_int1 <- (-agg_mc_int/agg_mc_slope)
agg_mc_slope1 <- (1/agg_mc_slope)

agg_mc_curve <- function(x){agg_mc_int1 + agg_mc_slope1*x}


optimal_tax_mc <- agg_mc_curve(300)
#39.43




#aggregate demand curve
#switch a slope and int to be in terms of q=
#a_demand_int1 <- (-a_demand_int/a_demand_slope)
#a_demand_slope1 <- (1/a_demand_slope)

#a_demand1 <- function(x){a_demand_int1 + a_demand_slope1*x}

#b slope and int to be in terms of q=
#b_demand_int1 <- (-b_demand_int/b_demand_slope)
#b_demand_slope1 <- (1/b_demand_slope)

#b_demand1 <- function(x){b_demand_int1 + b_demand_slope1*x}

#c slope and int to be in terms of q=
#c_demand_int1 <- (-c_demand_int/c_demand_slope)
#c_demand_slope1 <- (1/c_demand_slope)

#c_demand1 <- function(x){c_demand_int1 + c_demand_slope1*x}

#d slope and int to be in terms of q=
#d_demand_int1 <- (-d_demand_int/d_demand_slope)
#d_demand_slope1 <- (1/d_demand_slope)

#d_demand1 <- function(x){d_demand_int1 + d_demand_slope1*x}

#aggregate slope and intercept
#agg_demand_int <- sum(a_demand_int1,b_demand_int1,c_demand_int1)
#agg_demand_slope <- sum(a_demand_slope1, b_demand_slope1, c_demand_slope1)

#back in terms of p=
#agg_demand_int1 <- (-agg_demand_int/agg_demand_slope)
#agg_demand_slope1 <- (1/agg_demand_slope)

#agg_demand_curve <- function(x){agg_demand_int1 + agg_demand_slope1*x}

#optimal_tax <- agg_demand_curve(300)
#40.90 if you use aggregate demand, $39.43 if you use aggregate mc

agg_mc_plot <- ggplot(data.frame(x=c(0,200))) + 
  stat_function(fun=agg_mc_curve, geom="line", aes(color = "Aggregate Marginal Cost"))+
  scale_x_continuous(limits =c(0,350), expand = c(0,0))+
  scale_y_continuous(limits=c(0,200), expand=c(0,0))+
  theme_classic() +
  labs(fill = "", 
       color = "Sector",
       x = "Carbon Abatement (tons)",
       y = "Price ($/ton)")+
  ggtitle("Aggregate Marginal Cost of Abatement") 

agg_mc_plot

#emissions from sector A

a_abate <- a_curve1(optimal_tax_mc)
#abate 83.33 tons
a_emissions_tax <- 180-a_abate
#96.67 tons of CO2 

#cost of reduction for sector A
a_mc_abate <- a_curve(a_abate)
a_cost_abate <- integrate(a_curve, lower= 0, upper = a_abate)
#1282.61

#(0.5*(a_abate-a_x_int)*a_mc_abate)
  
a_tax_rev <- a_emissions_tax*optimal_tax_mc
#3811.18

#emissions from sector B

b_abate <- b_curve1(optimal_tax_mc)
#151.50
b_emissions_tax <- 200-b_abate
#48.50


#cost of reduction for sector B
b_mc_abate <- b_curve(b_abate)
b_cost_abate <- integrate(b_curve, lower= 0, upper = b_abate)
#3692.27

b_tax_rev <- b_emissions_tax*optimal_tax_mc
#1912.36
  
#(b_abate*0.5*(b_mc_abate+B_int))  


#emissions from sector C

c_abate <- c_curve1(optimal_tax_mc)
#65.17
c_emissions_tax <- 220-c_abate
#154.83

#cost of reduction for sector C
c_mc_abate <- c_curve(c_abate)
c_cost_abate<- integrate(c_curve, lower= 0, upper = c_abate)
#904.93

c_tax_rev <- c_emissions_tax*optimal_tax_mc
  
#(0.5*(c_abate-c_x_int)*a_mc_abate)
  


total_emissions <- sum(a_emissions_tax, b_emissions_tax, c_emissions_tax)
#300! wooooohooo

cost_total_abate<- a_cost_abate$value + b_cost_abate$value + c_cost_abate$value
#6175.09, why is this different than tax revenue?? is the difference a benefit to emitters? 

  
benefit_total <- sum(a_benefit_tax, b_benefit_tax, c_benefit_tax)
#6094.21

tax_rev <- optimal_tax_mc*300
#11827.97

#total costs+total benefits = tax revenue, does that make sense?

```


```{r}
#3c. Cap and trade. Each sector (A, B, C) is allocated carbon permits equal to their current emissions minus 100 (same as in (a) above), thus achieving the total reduction of 300. Then, these three sectors are allowed to trade with each other. You will need to derive the outcome of that trading.

#equimarginal principle: marginal cost of abatement must be the same across sectors to reach the efficient abatement goal 

#outcome of trading would result in the same amount of emissions as if a tax was imposed for each sector, the price of permits would be the same as the optimal tax

#only difference is the benefit of abatement = (100-emissions_tax)*optimal_tax

#benefit to A (will be a cost because they will end up emitting more than 100)
a_benefit_trade <- (80-a_emissions_tax)*optimal_tax_mc



#benefit to B (because they will emit less than 100 and sell extra permits)
b_benefit_trade <- (100-b_emissions_tax)*optimal_tax_mc


#benefit to C (will be a cost because they will end up emitting more than 1000)
c_benefit_trade <- (120-c_emissions_tax)*optimal_tax_mc


#A and B benefit from trade, C buys more credits 

```




4. Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon market. Doing so would require country Y to put a cap on carbon emissions at its current level of emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market?

```{r}

# because country Y has lower cost of abatement for carbon emissions above ~60 tons compared to sectors A and C, it would be beneficial for country Y to try to trade carbon credits. Similarly, country Y's WTP for the first few units of carbon emissions is lower than that of sector A and C. The incentive for country X to invite country Y into the market is that they would be able to "consume" more carbon emissions and avoid the increasing MC of abatement at high emissions levels


#add sector D to agg mc curve
Q_a_1 <- 1/A_slope
Q_a_2 <- A_int/A_slope
# Q for sector b
Q_b_1 <- 1/B_slope
Q_b_2 <- B_int/B_slope
# Q for sector C
Q_c_1 <- 1/C_slope
Q_c_2 <- C_int/C_slope
# Q for sector D
Q_d_1 <- 1/D_slope
Q_d_2 <- D_int/D_slope
# aggregate Qs
Q_agg_all_1 <- Q_a_1 + Q_b_1 + Q_c_1 + Q_d_1
Q_agg_all_2 <- Q_a_2 + Q_b_2 + Q_c_2 + Q_d_2


# make function of price
P_agg_all_1 <- 1/Q_agg_all_1
P_agg_all_2 <- Q_agg_all_2/Q_agg_all_1 # should this be negative
fun_agg_all <- function(x) P_agg_all_2 + P_agg_all_1*x
credit_price <- fun_agg_all(300)
#29.80



#find emissions for each sector

a_ct_abate <- a_curve1(credit_price)
#66.65
a_ct_emit <- 180-a_ct_abate
#113.35

b_ct_abate <- b_curve1(credit_price)
#103.07
b_ct_emit <- 200-b_ct_abate
#96.93

c_ct_abate <- c_curve1(credit_price)
#52.89
c_ct_emit <- 220-c_ct_abate
#167.11

d_ct_abate <- d_curve1(credit_price)
#77.38
d_ct_emit <- 300-d_ct_abate
#222.61

a_ct_benefit <- (100-a_ct_emit)*credit_price
#-397.84
a_ct_cost <- integrate(a_curve, 0, a_ct_abate)
#705.10

a_nb <- a_ct_benefit - a_ct_cost$value
#-1102.94

b_ct_benefit <- (100-b_ct_emit)*credit_price
#91.53
b_ct_cost <- integrate(b_curve, 0, b_ct_abate)
#2016.08

b_nb <- b_ct_benefit - b_ct_cost$value
#-1924.55


c_ct_benefit <- (100-c_ct_emit)*credit_price
#-2000.01
c_ct_cost <- integrate(c_curve, 0, c_ct_abate)
#479.92

c_nb <- c_ct_benefit - c_ct_cost$value
#-2479.93

d_ct_benefit <- (300-d_ct_emit)*credit_price
#2306.32
d_ct_cost <- integrate(d_curve, 0, d_ct_abate)
#1528.00

d_nb <- d_ct_benefit - d_ct_cost$value
#778.31


```

5. Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y.

a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y?

b. If country Y enters the carbon market for country X (as in question 4 above), how much local pollution will there be in country X and country Y?

c. What advice can you give country X and country Y about the desirability of allowing international trade of carbon emissions credits?


```{r}
#a. would expect 300 tons in country x and 300 tons in country y

#b.
pollution_x <- sum(a_ct_emit,b_ct_emit,c_ct_emit)
#377.39

pollution_y <- d_ct_emit
#222.61


#c. 
#if Country Y entered the cap and trade market, they would only emit 222.61 tons of carbon and would sell the rest of their credits to country X, meaning that country X would have more local pollution with country Y participating in the cap and trade program than with any of the three alternatives that considered just country X. 


```




